Power law properties of Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-03-20 tex/paper1/paper1.tex
adding plots in to the paper

\title{Collapsed Cores in Globular Clusters, \\
    Gauge-Boson Couplings, and AAS\TeX\ Examples}

@@

\author{S. Djorgovski\altaffilmark{1,2,3} and Ivan R. King\altaffilmark{1}}
\affil{Astronomy Department, University of California,
    Berkeley, CA 94720}

\author{C. D. Biemesderfer\altaffilmark{4,5}}
\affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
\email{aastex-help@aas.org}

@@

\author{R. J. Hanisch\altaffilmark{5}}
\affil{Space Telescope Science Institute, Baltimore, MD 21218}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
CTIO is operated by AURA, Inc.\ under contract to the National Science
Foundation.}
\altaffiltext{2}{Society of Fellows, Harvard University.}
\altaffiltext{3}{present address: Center for Astrophysics,
    60 Garden Street, Cambridge, MA 02138}
\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
\altaffiltext{5}{Patron, Alonso's Bar and Grill}

@@

\begin{abstract}
This is a preliminary report on surface photometry of the major
fraction of known globular clusters, to see which of them show the signs
of a collapsed core.
We also explore some diversionary mathematics and recreational tables.
\end{abstract}

@@

\keywords{globular clusters: general --- globular clusters: individual(NGC 6397,
NGC 6624, NGC 7078, Terzan 8}

@@

We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figures \ref{fig:loc171} and \ref{fig:loc193} show the location of the
regions on sample images from the time range considered.

\begin{figure}
\label{fig:loc171}

\begin{figure}
\label{fig:loc193}

@@

Figures \ref{fig:demo171} and \ref{fig:demo193} show example power
spectra, plotted using a log-log scale from individual pixels inside
each of the regions shown in Figures \ref{fig:loc171} and
\ref{fig:loc193}.  The shape of the power spectra indicate that the
Fourier power follows a power law approximately.

\begin{figure}
\label{fig:demo171}

\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (Figure \protect\ref{fig:loc171}).  The vertical black lines
  indicate the 3 and 5 minute frequencies. The equivalent plot in the
  AIA 193\AA\ waveband is shown in Figure \protect\ref{fig:demo193}.}
\end{figure}

\begin{figure}
\label{fig:demo193}

\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (Figure \protect\ref{fig:loc193}).  The vertical black lines
  indicate the 3 and 5 minute frequencies. The equivalent plot in the
  AIA 171\AA\ waveband is shown in Figure \protect\ref{fig:demo171}.}
\end{figure}

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of uncorrelated and incoherent Fourier power.  This suggests that a
second model for these regions should be considered.  The spectrum
$P_{1}$ where
\begin{equation}
\label{eq:pwrlawbunp}
\ln P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}
\end{equation}
contains the previous power law dependence, plus the second term,
modelling the excess power.

>>>>

\title{Power law properties of Fourier power spectra and their
  implications for coronal seismology and coronal heating.}

@@

\author{J. Ireland}
\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
  20771, USA. }
\email{jack.ireland@nasa.gov}

\author{R. T. J. McAteer}
\affil{Department of Astronomy, New Mexico State University, Las
  Cruces, NM}

@@

\author{A. R. Inglis}
\affil{Catholic University of America / NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
  20771, USA.}

@@

\begin{abstract}
The Fourier power spectra of regions of the solar corona are
investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
Fourier power spectra in all the regions show a power law behaviour
approximately.  This suggests that in many parts of the corona a
background model consisting of white noise and a trend cannot be
assumed when analyzing for the presence of oscillations in the corona.
Further, it is shown that the observed power law power spectrum is
consistent with that expected from summing a distribution of
exponentially decaying emission events along the line of sight.  This
is consistent with the notion that the corona is heated everywhere by
small energy deposition events, such as nanoflares.
\end{abstract}

@@

\keywords{???}

@@

We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figures \ref{fig:loc171193} show the location of the regions on sample
images from the time range considered.

\begin{figure}
\label{fig:loc171}
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_171.eps}
\caption{171 and 193}
\end{figure}

@@

Figures \ref{fig:compare171193} show example power spectra, plotted using
a log-log scale, from a single location inside each of the regions
shown in Figures \ref{fig:loc171} and \ref{fig:loc193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a power law at lower frequencies and flattens out at higher
frequencies.

\begin{figure}
\label{fig:compare171193}
\plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
\plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (see Figures \protect\ref{fig:loc171} and
  \protect\ref{fig:loc193}).  The vertical black lines indicate the 3
  and 5 minute frequencies.}
\end{figure}

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of uncorrelated and incoherent Fourier power.  This suggests that a
second model for these regions should be considered.  The spectrum
$P_{1}$ where
\begin{equation}
\label{eq:pwrlawbunp}
\ln P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
\end{equation}
contains the previous power law dependence, plus the second term,
modelling the excess power.
